Comparison of Catalogs

### 2024-07-25 compare/compare.qmd
b/k tab
pdf+rm warnings

---
title: "Comparison of Catalogs"
format: html
toc: true
toc-depth: 2
theme: minti
bibliography: ../My_Library.bib
execute: 
  echo: false
  eval: true
---

@@

1.  [$R^2$]{.underline}: Measures the proportion of variance explained by the linear model.
2.  [Slope of the Fitted Line]{.underline}: Should be close to 1 for a 1-1 correlation.[^1]
3.  [Pearson Correlation $\rho$]{.underline}: Measures the strength and direction of the linear relationship between two variables, ranging from -1 to 1. [^2]

@@

::: panel-tabset
# B mag
```{python}
scatter_plot(dt["mag_B"], dt["BT"], yerr = dt["E_BT"], sigma = True)
```

>>>>

---
title: "Comparison of Catalogs"
format: html
toc: true
toc-depth: 2
theme: minti
bibliography: ../My_Library.bib
execute: 
  echo: false
  eval: true
  warning: false
---

@@

1.  $R^2$: Measures the proportion of variance explained by the linear model.
2.  Slope of the Fitted Line: Should be close to 1 for a 1-1 correlation.[^1]
3.  Pearson Correlation $\rho$: Measures the strength and direction of the linear relationship between two variables, ranging from -1 to 1. [^2]

@@

::: panel-tabset
## B mag
```{python}
scatter_plot(dt["mag_B"], dt["BT"], yerr = dt["E_BT"], sigma = True)
```
